Overrelaxed Sinkhorn--Knopp Algorithm for Regularized Optimal Transport

### 2017-10-27 paper.tex
Relecture Nicolas

Formula \eqref{eq:kl_diff_scal} comes the expression $F(\gamma^1)-F(\gamma^2)= \sum_{i,j}\left(\gamma^*_{i,j}\log(\gamma^2_{i,j}/\gamma^1_{i,j})+\gamma^1_{i,j}-\gamma^2_{i,j}\right)$ and the relations \eqref{eq:def_or_proj} and \eqref{scaling}.
\end{proof}

>>>>

Formula \eqref{eq:kl_diff_scal} comes from the expression $F(\gamma^1)-F(\gamma^2)= \sum_{i,j}\left(\gamma^*_{i,j}\log(\gamma^2_{i,j}/\gamma^1_{i,j})+\gamma^1_{i,j}-\gamma^2_{i,j}\right)$ and the relations \eqref{eq:def_or_proj} and \eqref{scaling}.
\end{proof}
